---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "Arzu Aysin Tekindor"
date: "5/3/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

- Plot the logistic function from  `[-10,10]`

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

- Plot the Inverse Logistic function from `[0,1]`


**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }
#for graphs
x <- c(-10:10)
Beta0 = 0.5
intercept = 1
#formula
y <- 1/(1 + exp((Beta0 + intercept*x)))


library(ggplot2)
qplot(x,y)

#formula for inverse
y1 <- exp((Beta0 + intercept*x)) / (1 + exp((Beta0 + intercept*x)))

qplot (x,y1)


#functions
#Logistic
function1 <- function(Beta) { x <- c(-10:10)
Beta0 = 0.5
intercept = 1
y <- 1/(1 + exp((Beta0 + intercept*x)))
}

#Inverse Logistic

function2 <- function(Beta) { x <- c(-10:10)
Beta0 = 0.5
intercept = 1
y <- exp((Beta0 + intercept*x)) / (1 + exp((Beta0 + intercept*x)))
}
```


# NYCFlights Model

Using the rectangular data that you created from the earlier assignment and following theexample from the text and class, create a model for arr_delay >= 22 minutes. Describe/Explain each of the steps and show all work.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file to your repository.   
## Step 1: [Create data for the model] 
```{r "Model" }

library(caret)
library(knitr)
library(pROC)
# Columns not related to exercise performance.
col.nrel <- c("day", "hour", "minute", "lat", 
              "lon", "alt", "tz","dst","speed")

# Columns with near zero variance
nsv <- nearZeroVar(c, saveMetrics = TRUE)
col.nzvs <- rownames(nsv[nsv$nzv == TRUE, ])
# Update the training set with the remaining fields
col.drops <- c(col.nrel, col.nzvs)
data <- c[,!(names(c) %in% col.drops)]
col.names = colnames(data)

# Delete missing values.
data1 <- na.omit(data)
col.names
str(data1)

#Create a season variable
data1$season<-5
data1$season[data1$month<3 | data1$month==12] <- 1
data1$season[3<=data1$month & data1$month<=5] <- 2
data1$season[6<data1$month & data1$month<=8] <- 3
data1$season[9 <= data1$month & data1$month<=11] <- 4

# Convert "month" to factor
data1$season<-as.factor(data1$season)

```

## Step 2: [Create a sample] 
```{r "Step 2: [Create a sample]" }

sample<-data1[sample(nrow(data1), 10000), ]


```


## Step 3: [Create the dependant variable] 
```{r "Step 3: [Create the dependant variable]" }
sample$arr_delay22 <- ifelse(sample$arr_delay > 22,
1,0)
```
## Step 4: [Create model] 
```{r "Step 4: [Create model]" }
fit<-glm(formula = arr_delay22 ~ season+dep_delay  +  
  carrier+flight+ origin+ dep_delay+  air_time  + distance   + engine+ seats, family = binomial(link = "logit"),  data = sample)
summary(fit)
```

# Question:

Is this a good model?  (Write your answer here.)
I don't have a good model. I need to work more on it. 

# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.
