---
title: "Assingment NYC Flight Data"
author: "Arzu Aysin Tekindor"
date: "April 11, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. 
In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, 
`airports.csv`, `planes.csv` and `weather.csv`.  Join/merge these tables such 
that there is one rectangular table with one row for each flight. 


Put code in each of the sections provided.

## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
library(readr)
flight <- read_csv("~/CSX460/CSX460/02-building-blocks/02-exercise-nycflights/data/flights.csv")

```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
library(ggplot2)
hist(flight$arr_delay, col='blue',xlim=c(0, 500))
hist(flight$dep_delay, col='red', add=T)

```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
library(car)
library(lubridate)
var<-as.data.frame(flight[,c("year", "month","day","arr_delay")])
var$date<-with(var, ymd(sprintf('%04d%02d%02d', year, month, day)))
var1<-as.data.frame(var[,c("date","arr_delay")])
scatterplotMatrix(var1,spread=FALSE, smoother.args=list(lty=2), main="Scatter Plot Matrix")

```



## Create tables for Categorical Variables

Create a `table`, counting the flights by origin airports and carrier.

```{r}
library(dplyr)
Total<-flight%>%
  group_by(origin, carrier) %>% 
   tally()
Total

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}
airports <- read_csv("~/CSX460/CSX460/02-building-blocks/02-exercise-nycflights/data/airports.csv")
planes <- read_csv("~/CSX460/CSX460/02-building-blocks/02-exercise-nycflights/data/planes.csv")
weather <- read_csv("~/CSX460/CSX460/02-building-blocks/02-exercise-nycflights/data/weather.csv")

flight_planes <- left_join(flight, planes)

a<-dplyr::left_join(flight, planes, by = c( "tailnum"))
b<-dplyr::left_join(a, weather, by = c("origin", "time_hour"))

names(airports)[1] <- "origin"

c<-dplyr::left_join(a, airports, by = c("origin"))

str(c)

```



