---
title: "Caret / Recursive Partitioning"
author: "Your Name Here"
date: "Today's Date"
output: word_document
---

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
# .. Additional libraries
```


## Exercise 1: caret/logistic regression (5 points)

Rebuild your logistic regression model from the previous week, this time using the `caret` package. 

- Calculate the training or apparent performance of the model. 
- Calculate an unbiased measure of performance 
- Create a ROC Curve for your model

Show all work.

```{r logistic model}
#  Training 

data1$arr_delay22 <- ifelse(data1$arr_delay > 22,1,0)
data1$arr_delay221<- as.factor(data1$arr_delay22)
sample1<-data1[sample(nrow(data1), 10000), ]
Train <- createDataPartition(sample1$arr_delay22 , p=0.7, list=FALSE)
training <- sample1[ Train, ]
testing <- sample1[ -Train, ]

mod_fit <- train( as.factor(arr_delay22) ~ season+dep_delay  +  
  flight+ origin+ dep_delay+  air_time  + distance   + seats,  data=training, method="glm", family="binomial")

summary(mod_fit)
exp(coef(mod_fit$finalModel))
testp<-predict(mod_fit,testing,type='prob')[,2]
pred<-prediction(testp,testing$arr_delay22)
perf <-performance(pred,"tpr","fpr")

#performance
auc.perf = performance(pred, measure = "auc")
auc.perf@y.values



#Evaluation the performance
mod_fit_one <- glm(arr_delay22 ~ season+dep_delay  +  
  flight+ origin+ dep_delay+  air_time  + distance   + seats,   data=training, family="binomial")
mod_fit_two <- glm(arr_delay22 ~ season+dep_delay  +  
  flight+ origin+ dep_delay+  air_time  + distance   ,   data=training, family="binomial")

anova(mod_fit_one, mod_fit_two, test ="Chisq")

library(lmtest)
lrtest(mod_fit_one, mod_fit_two)


#ROC Curve
library(ROCR)
library(pROC)


plot(perf,col="green",lwd=2,main="ROC Curve for Logistic ")
abline(a=0,b=1,lwd=2,lty=2,col="gray")



```


## Exercise 2: caret/rpart (5 points)

Using the `caret` and `rpart` packages, create a **classification** model for flight delays using your NYC FLight data. Your solution should include:

- The use of `caret` and `rpart` to train a model.
- An articulation of the the problem your are 
- An naive model
- An unbiased calculation of the performance metric
- A plot of your model -- (the actual tree; there are several ways to do this)
- A discussion of your model 



Show and describe all work

```{r rpart model}
training$arr_delay222 <- factor(training$arr_delay22,levels=c(1,0),
                       labels=c("YES","NO")) 

library(party)
tree<-ctree(arr_delay222 ~ season+dep_delay  +  
  flight+  dep_delay+  air_time  + distance,data=training, control = ctree_control(mincriterion = 0.90,maxdepth=10))

plot(tree)


treepred <- as.data.frame(do.call("rbind", treeresponse(tree, newdata = testing)))
testing$tscore<-treepred[,1]
treepred<-prediction(testing$tscore,testing$arr_delay22)
treeperf <- performance(treepred,"tpr","fpr")

library(ROCR)
library(pROC)


plot(treeperf,col="green",lwd=2,main="ROC Curve for TREE ")
abline(a=0,b=1,lwd=2,lty=2,col="gray")

plot(treeperf,col='red',lwd=2, lty=1,main='ROC-Logistic vs Tree');
plot(perf, col='blue',lwd=2, add=TRUE,lty=2);
legend(0.6,0.6,c('Tree','Logistic'),col=c('red','blue'),lwd=2)
abline(a=0,b=1,lwd=2,lty=4,col="gray")
```


### Questions:

- Discuss the difference between the models and why you would use one model over the other?
- How might you produce an ROC type curve for the *rpart* model? 
