---
title: "NYCFlights: Arrival Delay Regression Model (Open Ended Variation)"
author: "Arzu Aysin Tekindor"
date: "April 18,2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NYCFlights Model

Using the rectangular data that you created last week create a model for `arr_delay`. Follow a well defined process for creating a model as discussed in class or from one of the readings. 

Break the process down into steps and create a codeblock for each step. 
 - Use as many steps you feel as necessary
 - Concisely explain each step 
 - Show all work
 
(You can start with the data that you created last week.)


## Step 1: [Data Wrangling and Preparation] 

```{r "Step 1: [Data Wrangling and Preparation]" }
library(caret)
library(knitr)
library(pROC)

# Columns not related to exercise performance.
col.nrel <- c("day", "hour", "minute", "lat", 
              "lon", "alt", "tz","dst","speed")
# Columns with near zero variance
nsv <- nearZeroVar(c, saveMetrics = TRUE)
col.nzvs <- rownames(nsv[nsv$nzv == TRUE, ])
# Update the training set with the remaining fields
col.drops <- c(col.nrel, col.nzvs)
data <- c[,!(names(c) %in% col.drops)]
col.names = colnames(data)

# Delete missing values.
data1 <- na.omit(data)
col.names
str(data1)

#Create a season variable
data1$season<-5
data1$season[data1$month<3 | data1$month==12] <- 1
data1$season[3<=data1$month & data1$month<=5] <- 2
data1$season[6<data1$month & data1$month<=8] <- 3
data1$season[9 <= data1$month & data1$month<=11] <- 4

# Convert "month" to factor
data1$season<-as.factor(data1$season)

```

## Step 2: [Create a sample] 
```{r "Step 1: [Create a sample]" }

sample<-data1[sample(nrow(data1), 10000), ]
```

## Step 3: [MODEL] 
```{r "Step 3: [MODEL]" }
fit<-lm(formula= arr_delay ~ season+dep_delay  +  
  carrier+flight+ origin+ dest+ dep_delay+  air_time  + distance   + engine+ seats,data=sample)
summary(fit)
```
# Question:
Is this a good model?  (My model was fine. I have many signigicant results.I created a season variable. I see that spring, summer and fall had positive effect on arrival delay comparing to winter. Distance, arrival time, seats and deperture delay have potisitive effect on arrival delay . R square is 0.89.)

